Dirac neutrino mass generation from Majorana messenger

### 2019-09-16 draft.tex
mc

In order to estimate the possible values for the parameters involved in the neutrino masses we consider the case where $\lambda_2$, $\lambda_4$, $\lambda_7 \ll 1$ and $m_\chi^2\equiv m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$, which leads to $a\approx b\gg c$. 
Taking into account that for the mentioned case $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m^2_\chi$, we have that
%
\begin{align*}
(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{\alpha}} y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
\end{align*}
%
and by furhter assuming $m_{\chi}^{2} \gg (\kappa_\alpha v_S)^2$ one finds 
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{16 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_\alpha}y^{*}_{j\alpha}\,, \\
& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right) \left( \frac{M_{\psi_\alpha}}{50\,\text{GeV}}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,. \nonumber
\end{align}
%
In this way, in addition to the loop suppression it is possible to 
have further suppression in the neutrino mass matrix for small values
of either $v_S$, $\lambda_8$ or $h_{i \alpha} y_{j\alpha}$.

@@

The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}. It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV. 
%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.

>>>>

In order to estimate the possible values for the parameters involved in the neutrino masses we consider the case where $\lambda_2$, $\lambda_4$, $\lambda_7 \ll 1$ and $m_\chi^2\equiv m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$, which leads to $a\approx b\gg c$. 
Taking into account that for the mentioned case $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m^2_\chi$, we have that
%
\begin{align*}
(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{\alpha}} y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
\end{align*}
%
and by further assuming $m_{\chi}^{2} \gg M_{\psi_{\alpha}}^2$ one finds 
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{16 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_\alpha}y^{*}_{j\alpha}\,, \\
& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right) \left( \frac{M_{\psi_\alpha}}{50\,\text{GeV}}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,. \nonumber
\end{align}
%
In this way, in addition to the loop suppression it is possible to 
have further suppression in the neutrino mass matrix for small values
of either $v_S$, $\lambda_8$ or $h_{i \alpha} y_{j\alpha}$.

@@

The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g_X$ are displayed in Fig.~\ref{fig:Neff}. It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g_D \gtrsim 60$ TeV. 
%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
